Lasso_RCI_Response

### 2024-05-21 Lasso_RCI_Response.Rmd
Pre scores only

#Extract Year From Intake Date
#Convert to Date
library("lubridate")
Mothership$Intake_1<-ymd(Mothership$Intake_1)
Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
Mothership<-mutate(Mothership,
                   TxYear = as.factor(TxYear),
                   TxYear = recode(TxYear,
                                   "1582"="2014"))

@@

    # co occuring disorders
    Co_Anx = as.factor(
      ifelse(Anxiety_C == 1 & Mood_D == 1 |
               Anxiety_C == 1 & BPD_P == 1 |
               Anxiety_C == 1 & Substance_D == 1 |
               Anxiety_C == 1 & Trauma_D == 1 |
               Anxiety_C == 1 & Eating_D ==1 |
               Anxiety_C == 1 & Psychotic_D ==1 |
               Anxiety_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Mood = as.factor(
      ifelse(Mood_C == 1 & Anxiety_D == 1 |
               Mood_C == 1 & BPD_P == 1 |
               Mood_C == 1 & Substance_D == 1 |
               Mood_C == 1 & Trauma_D == 1 |
               Mood_C == 1 & Eating_D ==1 |
               Mood_C == 1 & Psychotic_D ==1 |
               Mood_C == 1 & Somatic_D==1 , 1, 0)),
    Co_BPD = as.factor(
      ifelse(BPD_Co_C == 1 & Anxiety_D == 1 |
               BPD_Co_C == 1 & Mood_D == 1 |
               BPD_Co_C == 1 & Substance_D == 1 |
               BPD_Co_C == 1 & Trauma_D == 1 |
               BPD_Co_C == 1 & Eating_D ==1 |
               BPD_Co_C == 1 & Psychotic_D ==1 |
               BPD_Co_C == 1 & !BPD_P == 1 |
               BPD_Co_C == 1 & Somatic_D ==1 , 1, 0)),
    Co_Psychotic = as.factor(
      ifelse(Psychotic_C == 1 & Mood_D == 1 |
               Psychotic_C == 1 & BPD_P == 1 |
               Psychotic_C == 1 & Substance_D == 1 |
               Psychotic_C == 1 & Trauma_D == 1 |
               Psychotic_C == 1 & Eating_D ==1 |
               Psychotic_C == 1 & Anxiety_D ==1 |
               Psychotic_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Eating = as.factor(
      ifelse(Eating_C == 1 & Mood_D == 1 |
               Eating_C == 1 & BPD_P == 1 |
               Eating_C == 1 & Substance_D == 1 |
               Eating_C == 1 & Trauma_D == 1 |
               Eating_C == 1 & Psychotic_D ==1 |
               Eating_C == 1 & Anxiety_D ==1 |
               Eating_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Somatic =  as.factor(
      ifelse(Somatic_C == 1 & Mood_D == 1 |
               Somatic_C == 1 & BPD_P == 1 |
               Somatic_C == 1 & Substance_D == 1 |
               Somatic_C == 1 & Trauma_D == 1 |
               Somatic_C == 1 & Eating_D ==1 |
               Somatic_C == 1 & Anxiety_D ==1 |
               Somatic_C == 1 & Substance_D ==1 |
               Somatic_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Substance = as.factor(
      ifelse(Substance_C == 1 & Mood_D == 1 |
               Substance_C == 1 & BPD_P == 1 |
               Substance_C == 1 & Substance_D == 1 |
               Substance_C == 1 & Trauma_D == 1 |
               Substance_C == 1 & Eating_D ==1 |
               Substance_C == 1 & Anxiety_D ==1 |
               Substance_C == 1 & Somatic_D ==1 |
               Substance_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Trauma = as.factor(
      ifelse(Trauma_C == 1 & Mood_D == 1 |
               Trauma_C == 1 & BPD_P == 1 |
               Trauma_C == 1 & Substance_D == 1 |
               Trauma_C == 1 & Eating_D ==1 |
               Trauma_C == 1 & Anxiety_D ==1 |
               Trauma_C == 1 & Somatic_D ==1 |
               Trauma_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Other = as.factor(
      ifelse(
        Co_Substance == 1 |
        Co_Somatic == 1 |
        Co_Eating == 1 |
        Co_Psychotic == 1, 1, 0))
      )

##### df for plots

@@

#4 Adding it back to mother ship
    Mothership_post <- Mothership_post |>
      mutate(
        CUDOS_first = ifelse(is.na(BL_CUDOS),Pre_dep,BL_CUDOS),
        CUDOS_first = ifelse(CUDOS_first < 0, NA, CUDOS_first),
        CUXOS_first = ifelse(is.na(BL_CUXOS),Pre_anx,BL_CUXOS),
        CUXOS_first = ifelse(CUXOS_first < 0, NA, CUXOS_first),
        CUDOS_pre = BL_CUDOS,
        CUXOS_pre = BL_CUXOS,
        CUDOS_post = ifelse(!is.na(SUMdep_DC), SUMdep_DC,Post_Dep),
        CUDOS_post = ifelse(CUDOS_post < 0, NA, CUDOS_post),
        CUXOS_post = ifelse(!is.na(SUManx_DC), SUManx_DC,Post_anx),
        CUXOS_post = ifelse(CUXOS_post < 0, NA, CUXOS_post),
#5 Making some other varaibles
        BL_Missing = as.factor(ifelse(is.na(BL_CUXOS), "Anx Missing",
                                      ifelse(is.na(BL_CUDOS), "Dep Missing", "Not Missing"
                                      ))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                                  ifelse(BL_CUXOS > 20, "Sig Anx",
                                         ifelse(BL_CUDOS > 20, "Sig Dep",
                                                ifelse(is.na(BL_CUXOS),NA,
                                                       ifelse(is.na(BL_CUDOS),NA, "Sub Both"
                                                       )))))),
        Sig_BL_Anx = as.factor(ifelse(BL_CUXOS > 20, "Significant",
                                      ifelse(is.na(BL_CUXOS),NA, "Subclinical"
                                      ))),
        Sig_BL_Dep = as.factor(ifelse(BL_CUDOS > 20, "Significant",
                                      ifelse(is.na(BL_CUDOS),NA, "Subclinical"
                                      ))),
        Sig_Post_Anx = as.factor(ifelse(CUXOS_post > 20, "Significant",
                                        ifelse(is.na(CUXOS_post),NA, "Subclinical"
                                        ))),
        Sig_Post_Dep = as.factor(ifelse(CUDOS_post > 20, "Significant",
                                        ifelse(is.na(CUDOS_post),NA, "Subclinical"
                                        ))),
        Any_Sig_BL = as.factor(ifelse(BL_CUXOS > 20 | BL_CUDOS > 20, "Sig",
                                      ifelse(is.na(BL_CUXOS),NA,
                                             ifelse(is.na(BL_CUDOS),NA, "Sub"
                                             )))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                                  ifelse(BL_CUXOS > 20, "Sig Anx",
                                         ifelse(BL_CUDOS > 20, "Sig Dep",
                                                ifelse(is.na(BL_CUDOS), NA,
                                                       ifelse(is.na(BL_CUXOS), NA, "Subclinical"
                                                       ))))))
)
```

@@

JTRCI with less people
```{r}

Mothership_lasso <- Mothership_post |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  #!is.na(Anxiety_Responder),
  ) |>
  select( c(
    ID1,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    # rdqPRE_coping:rdqPRE_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
    #ACT stuff
    # AAQIIpre, AAQIIpost,
    # Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre,
    # Acting_mindful_pre,
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post,
  ))

@@

```{r}
RCI_df_anx2 <- Mothership_lasso_1 |>
  filter(
    !is.na(CUXOS_pre),
    !is.na(CUXOS_post),
    CUXOS_pre > 20,
  )|>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUXOS_pre),
    post = as.numeric(CUXOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

@@

```{r}
### Anxeity 
Mothership_lasso_anx <- Mothership_post_anx |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  !is.na(Anxiety_Responder),
  CUXOS_pre >= 20,
  ) |>
  select( c(
    ID1,Anxiety_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,rdqPRE_coping:rdqPRE_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
        #ACT stuff
    AAQIIpre, AAQIIpost, 
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post, FFMQ_post_total, 
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre, FFMQ_post_total
  ))
Mothership_lasso_anx <- na.omit(Mothership_lasso_anx)

### depression
Mothership_lasso_dep <- Mothership_post_dep |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Depression_Responder),
    CUDOS_pre >= 20,
  ) |>
  select( c(
    ID1, Depression_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,rdqPRE_coping:rdqPRE_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
    #ACT stuff
    AAQIIpre, AAQIIpost, 
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post, 
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre,

@@

#Delete ID1 from dfs
Mothership_lasso_anx <- Mothership_lasso_anx[,-1]
Mothership_lasso_dep <- Mothership_lasso_dep[,-1]
```

@@

Vars_dep <- Mothership_lasso_dep |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    #rdqPRE_coping:rdqPRE_wbs,
    #For table 3 - RCI info
    CUXOS_pre,CUDOS_pre, 
    #ACT stuff
    # AAQIIpre, AAQIIpost,
    #  Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    # Acting_mindful_pre, 
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post,
  ))

Vars_dep <- na.omit(Vars_dep)
```

@@

tmp_coeffs <- coef(lasso.model.min.dep, s = "lambda.min")
Dep_coefs <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
Dep_reg_coefs <- Dep_coefs[2:length(Dep_coefs)]
Dep_reg_coefs
```

@@

# min model - post AAQII no Mindful stuff
glm_min_dep <-
          glm(
    #Outcome varaible
      Depression_Responder ~
    # predictors
Days_not_attended_1 + Anxiety_C + BPD_Co_C + Current_Dx + 
  CUXOS_pre +  Non_react_post + 
  Self_compasion_post + Acting_mindful_post,
    #data
      data = Vars_dep,
    # type of regression : logistic = binary / binomial
      family = "binomial",
    )

@@

  #wald
   library(aod)
   # wald.test(b = coef(glm_min_dep),Sigma = vcov(glm_min_dep),Terms= 2:13)

@@

# Anxiety Lasso 
Preparing data for lasso - Anxiety
```{r}

Vars_anx <- Mothership_lasso_anx |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    #rdqPRE_coping:rdqPRE_wbs,
    #For table 3 - RCI info
    CUXOS_pre,CUDOS_pre, 
    #ACT stuff
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    Acting_mindful_post,
  ))

@@

coef(lasso.model.min.anx)
# Make prediction on test data
x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
probabilities <- lasso.model.min.anx %>% predict(newx = x.test,)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Anxiety_Responder
Mean.predict.min.anx <- mean(predicted.classes == observed.classes)

#####  using 1se
# Final model with lambda.1se
lasso.model.1se.anx <- glmnet(x, y, alpha = 1, family = "binomial",
                      lambda = cv.lasso.anx$lambda.1se,
                      standardized = TRUE)
coef(lasso.model.1se.anx)
# Make prediction on test data
x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
probabilities <- lasso.model.1se.anx %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")

@@

```{r}
## min model
  glm_min_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Age_1 + Some_College + Female + Married + White + Days_not_attended_1 + 
        BPD_Co_C + CUXOS_pre +  
        Non_react_post+  Self_compasion_post + Acting_mindful_post,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")

@@

FP_anx <- FP_anx |>
  mutate(
    sig = ifelse(p.adjusted <= 0.05, 16,1)
  )
```

>>>>

```{r}
#Extract Year From Intake Date
#Convert to Date
library("lubridate")
Mothership$Intake_1<-ymd(Mothership$Intake_1)
Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
Mothership<-mutate(Mothership,
                   TxYear = as.factor(TxYear),
                   TxYear = recode(TxYear,
                                   "1582"="2014"))

@@

    # co occuring disorders
    Co_Anx = as.factor(
      ifelse(Anxiety_C == 1 & Mood_D == 1 |
               Anxiety_C == 1 & BPD_P == 1 |
               Anxiety_C == 1 & Substance_D == 1 |
               Anxiety_C == 1 & Trauma_D == 1 |
               Anxiety_C == 1 & Eating_D ==1 |
               Anxiety_C == 1 & Psychotic_D ==1 |
               Anxiety_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Mood = as.factor(
      ifelse(Mood_C == 1 & Anxiety_D == 1 |
               Mood_C == 1 & BPD_P == 1 |
               Mood_C == 1 & Substance_D == 1 |
               Mood_C == 1 & Trauma_D == 1 |
               Mood_C == 1 & Eating_D ==1 |
               Mood_C == 1 & Psychotic_D ==1 |
               Mood_C == 1 & Somatic_D==1 , 1, 0)),
    Co_BPD = as.factor(
      ifelse(BPD_Co_C == 1 & Anxiety_D == 1 |
               BPD_Co_C == 1 & Mood_D == 1 |
               BPD_Co_C == 1 & Substance_D == 1 |
               BPD_Co_C == 1 & Trauma_D == 1 |
               BPD_Co_C == 1 & Eating_D ==1 |
               BPD_Co_C == 1 & Psychotic_D ==1 |
               BPD_Co_C == 1 & !BPD_P == 1 |
               BPD_Co_C == 1 & Somatic_D ==1 , 1, 0)),
    Co_Psychotic = as.factor(
      ifelse(Psychotic_C == 1 & Mood_D == 1 |
               Psychotic_C == 1 & BPD_P == 1 |
               Psychotic_C == 1 & Substance_D == 1 |
               Psychotic_C == 1 & Trauma_D == 1 |
               Psychotic_C == 1 & Eating_D ==1 |
               Psychotic_C == 1 & Anxiety_D ==1 |
               Psychotic_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Eating = as.factor(
      ifelse(Eating_C == 1 & Mood_D == 1 |
               Eating_C == 1 & BPD_P == 1 |
               Eating_C == 1 & Substance_D == 1 |
               Eating_C == 1 & Trauma_D == 1 |
               Eating_C == 1 & Psychotic_D ==1 |
               Eating_C == 1 & Anxiety_D ==1 |
               Eating_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Somatic =  as.factor(
      ifelse(Somatic_C == 1 & Mood_D == 1 |
               Somatic_C == 1 & BPD_P == 1 |
               Somatic_C == 1 & Substance_D == 1 |
               Somatic_C == 1 & Trauma_D == 1 |
               Somatic_C == 1 & Eating_D ==1 |
               Somatic_C == 1 & Anxiety_D ==1 |
               Somatic_C == 1 & Substance_D ==1 |
               Somatic_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Substance = as.factor(
      ifelse(Substance_C == 1 & Mood_D == 1 |
               Substance_C == 1 & BPD_P == 1 |
               Substance_C == 1 & Substance_D == 1 |
               Substance_C == 1 & Trauma_D == 1 |
               Substance_C == 1 & Eating_D ==1 |
               Substance_C == 1 & Anxiety_D ==1 |
               Substance_C == 1 & Somatic_D ==1 |
               Substance_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Trauma = as.factor(
      ifelse(Trauma_C == 1 & Mood_D == 1 |
               Trauma_C == 1 & BPD_P == 1 |
               Trauma_C == 1 & Substance_D == 1 |
               Trauma_C == 1 & Eating_D ==1 |
               Trauma_C == 1 & Anxiety_D ==1 |
               Trauma_C == 1 & Somatic_D ==1 |
               Trauma_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Other = as.factor(
      ifelse(
        Co_Substance == 1 |
        Co_Somatic == 1 |
        Co_Eating == 1 |
        Co_Psychotic == 1, 1, 0))
      )
summary(as.factor(Mothership$Prev_AdmitID_1))
view(Mothership)
```

```{r}
##### df for plots

@@

#4 Adding it back to mother ship
    Mothership_post <- Mothership_post |>
      mutate(
        CUDOS_first = ifelse(is.na(BL_CUDOS),Pre_dep,BL_CUDOS),
        CUDOS_first = ifelse(CUDOS_first < 0, NA, CUDOS_first),
        CUXOS_first = ifelse(is.na(BL_CUXOS),Pre_anx,BL_CUXOS),
        CUXOS_first = ifelse(CUXOS_first < 0, NA, CUXOS_first),
        CUDOS_pre = BL_CUDOS,
        CUXOS_pre = BL_CUXOS,
        CUDOS_post = ifelse(!is.na(SUMdep_DC), SUMdep_DC,Post_Dep),
        CUDOS_post = ifelse(CUDOS_post < 0, NA, CUDOS_post),
        CUXOS_post = ifelse(!is.na(SUManx_DC), SUManx_DC,Post_anx),
        CUXOS_post = ifelse(CUXOS_post < 0, NA, CUXOS_post),
#5 Making some other varaibles
        BL_Missing = as.factor(ifelse(is.na(BL_CUXOS), "Anx Missing",
                                      ifelse(is.na(BL_CUDOS), "Dep Missing", "Not Missing"
                                      ))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                                  ifelse(BL_CUXOS > 20, "Sig Anx",
                                         ifelse(BL_CUDOS > 20, "Sig Dep",
                                                ifelse(is.na(BL_CUXOS),NA,
                                                       ifelse(is.na(BL_CUDOS),NA, "Sub Both"
                                                       )))))),
        Sig_BL_Anx = as.factor(ifelse(BL_CUXOS > 20, "Significant",
                                      ifelse(is.na(BL_CUXOS),NA, "Subclinical"
                                      ))),
        Sig_BL_Dep = as.factor(ifelse(BL_CUDOS > 20, "Significant",
                                      ifelse(is.na(BL_CUDOS),NA, "Subclinical"
                                      ))),
        Sig_Post_Anx = as.factor(ifelse(CUXOS_post > 20, "Significant",
                                        ifelse(is.na(CUXOS_post),NA, "Subclinical"
                                        ))),
        Sig_Post_Dep = as.factor(ifelse(CUDOS_post > 20, "Significant",
                                        ifelse(is.na(CUDOS_post),NA, "Subclinical"
                                        ))),
        Any_Sig_BL = as.factor(ifelse(BL_CUXOS > 20 | BL_CUDOS > 20, "Sig",
                                      ifelse(is.na(BL_CUXOS),NA,
                                             ifelse(is.na(BL_CUDOS),NA, "Sub"
                                             )))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                                  ifelse(BL_CUXOS > 20, "Sig Anx",
                                         ifelse(BL_CUDOS > 20, "Sig Dep",
                                                ifelse(is.na(BL_CUDOS), NA,
                                                       ifelse(is.na(BL_CUXOS), NA, "Subclinical"
                                                       ))))))
)

@@

JTRCI with less people
```{r}
Mothership_Missing <- Mothership_post |>
  select(
    ID1, 
    # RDQ
    rdqPRE_coping:rdqPRE_wbs,
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post,CUDOS_pre, CUDOS_post, 
    #ACT stuff
    AAQIIpre,AAQIIpost,
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre, 
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post, 
    Acting_mindful_post 
  )

#install.packages('naniar')
library(naniar)
vis_miss(Mothership_Missing)
```

```{r}
Mothership_lasso <- Mothership_post |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  #!is.na(Anxiety_Responder),
  ) |>
  select( c(
    ID1,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPRE_coping:rdqPRE_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
    #ACT stuff
    AAQIIpre, #AAQIIpost,
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre,
    Acting_mindful_pre,
    # Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    # Acting_mindful_post,
  ))

@@

```{r}
library(JTRCI)
RCI_df_anx2 <- Mothership_lasso_1 |>
  filter(
    !is.na(CUXOS_pre),
    !is.na(CUXOS_post),
    CUXOS_pre > 20,
  )|>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUXOS_pre),
    post = as.numeric(CUXOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

@@

```{r}
### Anxeity 
Mothership_lasso_anx <- Mothership_post_anx |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  !is.na(Anxiety_Responder),
  CUXOS_pre >= 20,
  ) |>
  select( c(
    ID1,Anxiety_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPRE_coping:rdqPRE_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
    #ACT stuff
    AAQIIpre,
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre, 
  ))

Mothership_lasso_anx <- na.omit(Mothership_lasso_anx)

dim(Mothership_lasso_anx)
### depression
Mothership_lasso_dep <- Mothership_post_dep |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Depression_Responder),
    CUDOS_pre >= 20,
  ) |>
  select( c(
    ID1, Depression_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPRE_coping:rdqPRE_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
    #ACT stuff
    AAQIIpre,
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre,

@@

#Delete ID1 from dfs
Mothership_lasso_anx <- Mothership_lasso_anx[,-1]
Mothership_lasso_dep <- Mothership_lasso_dep[,-1]

@@

Vars_dep <- Mothership_lasso_dep |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPRE_coping:rdqPRE_wbs,
    #For table 3 - RCI info
    CUXOS_pre,CUDOS_pre, 
    #ACT stuff
    AAQIIpre,
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre,

  ))

Vars_dep <- na.omit(Vars_dep)
dim(Vars_dep)
```

@@

tmp_coeffs <- coef(lasso.model.1se.dep, s = "lambda.1se")
Dep_coefs <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
Dep_reg_coefs <- Dep_coefs[2:length(Dep_coefs)]
Dep_reg_coefs
```

@@

Vars_dep <- Vars_dep |>
  mutate(
    YA_Treatment = as.factor(ifelse(IPT_track_1 == "Young Adult",1,0)),
    Trauma_Treatment = as.factor(ifelse(IPT_track_1 == "Trauma",1,0))
  )

# min model - post AAQII no Mindful stuff
glm_min_dep <-
          glm(
    #Outcome varaible
      Depression_Responder ~
    # predictors
      Some_College + Female + White + YA_Treatment + Trauma_Treatment + Days_complete_1 + 
      Days_not_attended_1 + Anxiety_D + BPD_P+ Trauma_D+Other+ Anxiety_C + Mood_C+ 
      BPD_Co_C + Substance_C + No_Co + Current_Dx + CUXOS_pre + rdqPRE_coping + 
      rdqPRE_pmh + rdqPRE_func + AAQIIpre + Self_compasion_pre,
    #data
      data = Vars_dep,
    # type of regression : logistic = binary / binomial
      family = "binomial",
    )

@@

  #wald
   library(aod)
   wald.test(b = coef(glm_min_dep),Sigma = vcov(glm_min_dep),Terms= 2:24)

@@

# Anxiety Lasso 
Preparing data for lasso - Anxiety
```{r}
Vars_anx <- Mothership_lasso_anx |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPRE_coping:rdqPRE_wbs,
    #For table 3 - RCI info
    CUXOS_pre,CUDOS_pre, 
    #ACT stuff
    AAQIIpre,
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre, 
  ))

@@

coef(lasso.model.min.anx)
# Make prediction on test data
x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
probabilities <- lasso.model.min.anx %>% predict(newx = x.test,type="response")
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Anxiety_Responder
Mean.predict.min.anx <- mean(predicted.classes == observed.classes)

#####  using 1se
# Final model with lambda.1se
lasso.model.1se.anx <- glmnet(x, y, alpha = 1, family = "binomial",
                      lambda = cv.lasso.anx$lambda.1se,
                      standardized = TRUE)
coef(lasso.model.1se.anx)
# Make prediction on test data
x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
probabilities <- lasso.model.1se.anx %>% predict(newx = x.test,type="response")
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")

@@

```{r}
## min model

Vars_anx <- Vars_anx |>
  mutate(
    YA_Treatment = as.factor(ifelse(IPT_track_1 == "Young Adult",1,0)),
    Trauma_Treatment = as.factor(ifelse(IPT_track_1 == "Trauma",1,0))
  )

  glm_min_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Age_1 + Female + Married + White + YA_Treatment + Trauma_Treatment + 
        Days_complete_1 + Days_not_attended_1 + Anxiety_D + Mood_C + Trauma_C + 
        Substance_C + Current_Dx + CUDOS_pre + rdqPRE_coping + rdqPRE_func + 
        AAQIIpre + Non_react_pre + Self_compasion_pre,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")

@@

FP_anx <- FP_anx |>
  mutate(
    sig = ifelse(p.adjusted <= 0.05, 16,1)
  )
